Machine learning high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2023-03-13 mc.tex
briefly describe FOAM algorithm

    From this description, it is clear that the number
    of accepted events will generally be lower than
    the number of total events generated. This is encapsulated
    in the unweighting efficiency
    \begin{equation}\label{eqn:unweighting_efficiency}
        \epsilon = \dfrac{N_{\mathrm{accepted}}}{N_{\mathrm{total}}} \, ,
    \end{equation}
    whose inverse is the average number of trial
    events required to obtain a single unweighted event.
    Unweighting efficiencies for high-multiplicity processes
    are often well below 1\% \cite{Hoche:2019flt,Gao:2020zvv} and the development
    of methods to improve the efficiency are an active area of research
    \cite{Jadach:1999sf,Jadach:2002kn}.
    These low efficiencies lead to most of the
    yearly event generator CPU budgets of LHC experiments to be spent on
    unweighting events \cite{HSFPhysicsEventGeneratorWG:2020gxw}.

>>>>

    From this description, it is clear that the number
    of accepted events will generally be lower than
    the number of total events generated. This is encapsulated
    in the unweighting efficiency
    \begin{equation}\label{eqn:unweighting_efficiency}
        \epsilon = \dfrac{N_{\mathrm{accepted}}}{N_{\mathrm{total}}} \, ,
    \end{equation}
    whose inverse is the average number of trial
    events required to obtain a single unweighted event.
    Unweighting efficiencies for high-multiplicity processes
    are often well below 1\% \cite{Hoche:2019flt,Gao:2020zvv}.
    The development of methods to improve the efficiency are an active
    area of research \cite{Jadach:1999sf,Jadach:2002kn}, wherein the
    authors explore an algorithm that adaptively splits up the integration
    region in order to systematically reduce the ratio of
    the maximum event weight to the average event weight. This leads to
    increased unweighting efficiency when carrying out the rejection sampling
    algorithm.
    These low efficiencies lead to most of the
    yearly event generator CPU budgets of LHC experiments to be spent on
    unweighting events \cite{HSFPhysicsEventGeneratorWG:2020gxw}.
